Predictions

### 2021-03-27 analysis/02_descriptive-analysis.Rmd
{targets}ification

---
title: "Descriptive analysis"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
params:
  fig_width: 6
  fig_height: 3.6
  fig_height_taller: 5
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(brms)
library(broom)
library(tidybayes)
library(sf)
library(scico)
library(scales)
library(patchwork)
library(ggtext)
library(here)

@@

canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))

# https://www.naturalearthdata.com/downloads/110m-cultural-vectors/
country_borders <- read_sf(here("data", "raw_data", "Natural Earth", 
                                "ne_110m_admin_0_countries", 
                                "ne_110m_admin_0_countries.shp"))
```

@@

map_data <- country_borders %>% 
  left_join(things_to_map, by = c("ADM0_A3_IS" = "iso3")) %>% 
  filter(ISO_A3 != "ATA")
```

@@

```{r map-ngo-laws, fig.width=params$fig_width, fig.height=params$fig_height_taller}
map_ngo_laws <- ggplot() +
  geom_sf(data = map_data, aes(fill = factor(new_laws)),
          color = "black", size = 0.1) +
  coord_sf(crs = 54030, datum = NA, expand = FALSE) + 
  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 7)), 
                    na.value = "grey80", breaks = 0:6) +
  # scale_fill_manual(values = scico(7, palette = "devon", direction = -1), 
  #                   na.value = "grey80", breaks = 0:6) +
  guides(fill = guide_legend(nrow = 1, label.position = "bottom",
                             keywidth = unit(1, units = "lines"),
                             keyheight = unit(0.6, units = "lines"))) +
  labs(fill = "Restrictive NGO laws passed between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.spacing.x = unit(0, "pt"),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(10, "lines"),
                                              padding = margin(r = 10)))
map_ngo_laws
```

@@

```{r map-cs-repression, fig.width=params$fig_width, fig.height=params$fig_height_taller}
map_cs_repression <- ggplot() +
  geom_sf(data = map_data, aes(fill = diff_csrepress_trunc),
          color = "black", size = 0.1) +
  coord_sf(crs = 54030, datum = NA, expand = FALSE) + 
  scale_fill_scico(palette = "vik", direction = -1,
                   limits = c(-1, 1) * max(abs(map_data$diff_csrepress_trunc), na.rm = TRUE),
                   breaks = seq(-4, 4, 1), na.value = "grey80") +
  guides(fill = guide_colorbar(reverse = TRUE, ticks = FALSE,
                               barwidth = unit(7, units = "lines"),
                               barheight = unit(0.5, units = "lines"))) +
  labs(fill = "Change in V-Dem civil society repression between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(12, "lines"),
                                              padding = margin(r = 10)))
map_cs_repression
```

@@

```{r model-pts-cs, cache=TRUE, message=FALSE, results="hide"}
diff_cs_pts <- brm(
  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_pts")
)
```

@@

```{r plot-draws-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height}
ggplot(diff_cs_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  geom_halfeyeh() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()

# ggsave("~/Desktop/plot1.pdf", device = cairo_pdf, width = 5, height = 3, units = "in")
# ggsave("~/Desktop/plot1.png", type = "cairo", dpi = 300, width = 6, height = 3.6, units = "in")
```

@@

```{r vdem-suparna-plot, warning=FALSE, message=FALSE, fig.width=params$fig_width, fig.height=params$fig_height_taller}
canary_barriers <- canary %>% 
  pivot_longer(cols = c(advocacy, entry, funding, barriers_total), 
               names_to = "barrier", values_to = "count") %>% 
  mutate(barrier = recode(barrier, advocacy = "Barriers to advocacy",
                          entry = "Barriers to entry", 
                          funding = "Barriers to funding",
                          barriers_total = "Total NGO barriers"))

@@

```{r model-pts-restrictions, cache=TRUE, message=FALSE, warning=FALSE, results="hide"}
diff_ngo_pts <- brm(
  bf(barriers_total ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = select(canary, barriers_total, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_ngo_pts")
)
```

@@

```{r plot-draws-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height}
ggplot(diff_ngo_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  geom_halfeyeh() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_ngo_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

```{r model-conflict-cs, cache=TRUE, message=FALSE, results="hide"}
diff_cs_conflict <- brm(
  bf(v2csreprss ~ 0 + armed_conflict, sigma ~ 0 + armed_conflict),
  family = student,
  data = select(canary, v2csreprss, armed_conflict),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_conflict")
)
```

@@

```{r plot-draws-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height}
ggplot(diff_cs_conflict_draws, aes(y = .variable, x = .value, fill = .variable)) + 
  geom_halfeyeh() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict") +
  theme_ngo()
```

```{r plot-posterior-preds-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_conflict_posterior, aes(x = .prediction, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()

# ggsave("~/Desktop/plot1.pdf", device = cairo_pdf, width = 5, height = 3, units = "in")
# ggsave("~/Desktop/plot1.png", type = "cairo", dpi = 300, width = 6, height = 3.6, units = "in")
```

@@

```{r repression-matrix, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
library(GGally)
repression_only <- canary %>% 
  filter(year == 2014) %>% 
  select(barriers_total, PTS, gh_alljourn, 
         v2clacfree, v2csrlgrep, v2mecenefm, v2mecenefi, v2meharjrn, v2meslfcen,
         v2x_clphy, v2x_clpol, v2x_clpriv, v2x_freexp, v2csreprss)

>>>>

---
title: "Descriptive analysis"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(broom)
library(tidybayes)
library(sf)
library(scico)
library(scales)
library(patchwork)
library(ggtext)
library(here)

@@

# Generated via random.org
set.seed(9936)

# Load data
# Need to use this withr thing because tar_read() and tar_load() need to see the
# _targets folder in the current directory, but this .Rmd file is in a subfolder
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  canary <- tar_read(panel_done_trimmed)
  tar_load(world_map)
})
```

@@

map_data <- world_map %>% 
  left_join(things_to_map, by = c("ADM0_A3_IS" = "iso3"))
```

@@

```{r map-ngo-laws}
map_ngo_laws <- ggplot() +
  geom_sf(data = map_data, aes(fill = factor(new_laws)),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 7)), 
                    na.value = "grey80", breaks = 0:6) +
  # scale_fill_manual(values = scico(7, palette = "devon", direction = -1), 
  #                   na.value = "grey80", breaks = 0:6) +
  guides(fill = guide_legend(nrow = 1, label.position = "bottom",
                             keywidth = unit(1, units = "lines"),
                             keyheight = unit(0.6, units = "lines"))) +
  labs(fill = "Restrictive NGO laws passed between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.spacing.x = unit(0, "pt"),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(10, "lines"),
                                              padding = margin(r = 10)))
map_ngo_laws
```

@@

```{r map-cs-repression}
map_cs_repression <- ggplot() +
  geom_sf(data = map_data, aes(fill = diff_csrepress_trunc),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_scico(palette = "vik", direction = -1,
                   limits = c(-1, 1) * max(abs(map_data$diff_csrepress_trunc), na.rm = TRUE),
                   breaks = seq(-4, 4, 1), na.value = "grey80") +
  guides(fill = guide_colorbar(reverse = TRUE, ticks = FALSE,
                               barwidth = unit(7, units = "lines"),
                               barheight = unit(0.5, units = "lines"))) +
  labs(fill = "Change in V-Dem civil society repression between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(12, "lines"),
                                              padding = margin(r = 10)))
map_cs_repression
```

@@

```{r model-pts-cs, message=FALSE, results="hide"}
diff_cs_pts <- brm(
  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_pts")
)
```

@@

```{r plot-draws-pts-cs}
ggplot(diff_cs_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  stat_halfeye() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-cs, warning=FALSE, message=FALSE}
ggplot(diff_cs_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dots(quantiles = 100, shape = 19) +
  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

```{r vdem-suparna-plot, warning=FALSE, message=FALSE}
canary_barriers <- canary %>% 
  pivot_longer(cols = c(advocacy, entry, funding, barriers_total), 
               names_to = "barrier", values_to = "count") %>% 
  mutate(barrier = recode(barrier, advocacy = "Barriers to advocacy",
                          entry = "Barriers to entry", 
                          funding = "Barriers to funding",
                          barriers_total = "Total NGO barriers"))

@@

```{r model-pts-restrictions, message=FALSE, warning=FALSE, results="hide"}
diff_ngo_pts <- brm(
  bf(barriers_total ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = select(canary, barriers_total, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_ngo_pts")
)
```

@@

```{r plot-draws-pts-ngo}
ggplot(diff_ngo_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  stat_halfeye() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-ngo, warning=FALSE, message=FALSE}
ggplot(diff_ngo_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dots(quantiles = 100, shape = 19) +
  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

```{r model-conflict-cs, message=FALSE, results="hide"}
diff_cs_conflict <- brm(
  bf(v2csreprss ~ 0 + armed_conflict, sigma ~ 0 + armed_conflict),
  family = student,
  data = select(canary, v2csreprss, armed_conflict),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_conflict")
)
```

@@

```{r plot-draws-conflict-cs}
ggplot(diff_cs_conflict_draws, aes(y = .variable, x = .value, fill = .variable)) + 
  stat_halfeye() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict") +
  theme_ngo()
```

```{r plot-posterior-preds-conflict-cs, warning=FALSE, message=FALSE}
ggplot(diff_cs_conflict_posterior, aes(x = .prediction, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
  stat_dots(quantiles = 100, shape = 19) +
  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

```{r repression-matrix, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
library(GGally)
repression_only <- canary %>% 
  filter(year == 2014) %>% 
  select(barriers_total, PTS, gh_alljourn, 
         v2clacfree, v2csrlgrep, v2mecenefm, v2meharjrn, v2meslfcen,
         v2x_clphy, v2x_clpol, v2x_clpriv, v2x_freexp, v2csreprss)

### 2021-03-27 analysis/03_models.Rmd
{targets}ification

---
title: "Models"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(broom)
library(here)
library(brms)
library(lme4)

@@

canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
canary_lagged <- read_rds(here("data", "derived_data", "canary_clean_lagged.rds"))
```

@@

@@

model_asdf <- lmer(PTS_lead1 ~  # Overall terror/repression level
                     v2csreprss_within + v2csreprss_between +  # Civil society repression
                     v2x_polyarchy_within + v2x_polyarchy_between +  # Democracy
                     gdpcap_log_within + gdpcap_log_between +  # GDP per capita
                     armed_conflict +  # Government involved in conflict with 25+ battle deaths
                     splines::bs(year) +  # Non-linear year trend
                     (1 + v2csreprss_within | region/gwcode) +  # Random slopes for within CS repression
                     (1 + v2csreprss_between | region/gwcode),  # Random slopes for between CS repression
                   data = canary_demeaned)

tidy(model_asdf, effects = "fixed")
coef(model_asdf)$`gwcode:region` %>% rownames_to_column() %>% as_tibble() %>% head()
coef(model_asdf)$region %>% rownames_to_column() %>% as_tibble()
```

```{r}
model_lag1 <- lm(PTS_lead1 ~ barriers_total + v2x_polyarchy + region + gdpcap_log + as.factor(year),
                 data = canary_lagged)
tidy(model_lag1)

modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss + v2x_polyarchy + region + gdpcap_log + as.factor(year),
                 data = canary_lagged)
tidy(modelx_lag1)

modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss,
                 data = canary_lagged)
tidy(modelx_lag1)
```

```{r}
thing1 <- brm(
  bf(PTS_lead1 ~ v2csreprss + v2x_polyarchy + region + gdpcap_log + 
       year + (1 + year | gwcode)),
  family = gaussian, inits = 0,
  control = list(adapt_delta = 0.99),
  data = canary_lagged %>% select(PTS_lead1, v2csreprss, v2x_polyarchy, 
                                  region, gdpcap_log, year, gwcode),
  prior = c(set_prior("normal(0, 10)", class = "Intercept"),
            set_prior("normal(0, 2.5)", class = "b"),
            set_prior("normal(0, 2.5)", class = "sd")),
  chains = CHAINS, iter = 8000, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "thing_8000")
)

@@

diff_cs_pts <- brm(
  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student, 
  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_pts")
)

tidy(thing)

lag1 <- lm(I(sqrt(terrorinclead) - coef(out)["totspendrevlog"]*totspendrevlog) ~ l(totspendrevlog, cow)  + l(govleft, cow) + l(democ, cow) + l(poplog, cow) + l(govcap, cow) + l(conflict, cow) + l(tradelog, cow) + europe +africa + asia + america + sqrt(l(terrorinc, cow))+ sqrt(l(terrorinc, cow, 2))+ as.factor(year), data=reasonabledata)

lag2 <- lm(I(sqrt(terrorinclead) - coef(out)["totspendrevlog"]*totspendrevlog - coef(lag1)["l(totspendrevlog, cow)"]*l(totspendrevlog, cow))~l(totspendrevlog, cow, 2)  + l(govleft, cow, 2) + l(democ, cow, 2) + l(democ, cow, 3) + l(poplog, cow, 2) + l(govcap, cow, 2) + l(conflict, cow, 2) + l(tradelog, cow, 2) + europe +africa + asia + america + sqrt(l(terrorinc, cow, 2))+ sqrt(l(terrorinc, cow,3))+ as.factor(year), data=reasonabledata)
```

>>>>

---
title: "Models"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(broom.mixed)
library(here)
library(brms)
library(lme4)
library(modelsummary)

@@

# Generated via random.org
set.seed(9936)

# Load data
# Need to use this withr thing because tar_read() and tar_load() need to see the
# _targets folder in the current directory, but this .Rmd file is in a subfolder
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  canary <- tar_read(panel_done_trimmed)
  canary_lagged <- tar_read(panel_lagged_trimmed)
})
```

@@

**I ran all these models in March 2020 pre-pandemic and I have no idea why??**

@@

model_asdf <- lmer(PTS_lead1 ~  # Overall terror/repression level
                     v2csreprss_within + v2csreprss_between +  # Civil society repression
                     v2x_polyarchy_within + v2x_polyarchy_between +  # Democracy
                     gdpcap_log_within + gdpcap_log_between +  # GDP per capita
                     armed_conflict +  # Government involved in conflict with 25+ battle deaths
                     splines::bs(year) +  # Non-linear year trend
                     (1 + v2csreprss_within | gwcode) +  # Random slopes for within CS repression
                     # (1 + v2csreprss_within | region/gwcode) +  # Random slopes for within CS repression
                     (1 + v2csreprss_between | gwcode),  # Random slopes for within CS repression
                     # (1 + v2csreprss_between | region/gwcode),  # Random slopes for between CS repression
                   data = canary_demeaned)

# modelsummary(list(model_asdf))
tidy(model_asdf, effects = "fixed")
# coef(model_asdf)$`gwcode` %>% rownames_to_column() %>% as_tibble() %>% head()
# coef(model_asdf)$region %>% rownames_to_column() %>% as_tibble()
```

```{r}
model_lag1 <- lm(PTS_lead1 ~ barriers_total + v2x_polyarchy + gdpcap_log + as.factor(year),
                 data = canary_lagged)

modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss + v2x_polyarchy + gdpcap_log + as.factor(year),
                 data = canary_lagged)

modelxx_lag1 <- lm(PTS_lead1 ~ v2csreprss,
                   data = canary_lagged)

modelsummary(list(model_lag1, modelx_lag1, modelxx_lag1),
             coef_omit = "^as.factor",
             stars = TRUE, gof_omit = "IC|F|Log.|R2$") %>% 
  row_spec(10, extra_css = "border-bottom: 2px solid")
```

**¿What even is this stuff?**

```{r eval=FALSE}
thing1 <- brm(
  bf(PTS_lead1 ~ v2csreprss + v2x_polyarchy + region + gdpcap_log + 
       year + (1 + year | gwcode)),
  family = gaussian, inits = 0,
  control = list(adapt_delta = 0.99),
  data = canary_lagged %>% select(PTS_lead1, v2csreprss, v2x_polyarchy, 
                                  region, gdpcap_log, year, gwcode),
  prior = c(set_prior("normal(0, 10)", class = "Intercept"),
            set_prior("normal(0, 2.5)", class = "b"),
            set_prior("normal(0, 2.5)", class = "sd")),
  chains = CHAINS, iter = 8000, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "thing_8000")
)

@@

diff_cs_pts <- brm(
  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student, 
  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_pts")
)
```

### 2021-03-27 analysis/04_predictions.Rmd
{targets}ification

---
title: "Predictions"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)

canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
```

>>>>

---
title: "Predictions"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(here)

# Load data
# Need to use this withr thing because tar_read() and tar_load() need to see the
# _targets folder in the current directory, but this .Rmd file is in a subfolder
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  canary <- tar_read(panel_done_trimmed)
})
```
